Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-04-03 doc/supplementary_information.Rmd
supplementary with updated clim figs

```{r read files, echo=F}
# Read in files
```

@@

![](../results/plots/climate_data_timeseries_2007_2019.png)

![](../results/plots/climate_data_correlations.png)

<!-- ![](display/env_vars_SI.png) -->

@@

@@

## Individual correlations

@@

## Individual model diagnostics

## Additional models

>>>>

```{r read files, echo=F}
# Read in files

# figure numbers

# figure titles
```

@@

![Figure S1: Raw climate data timeseries](display/climvars_fullseries.png)

![Figure S2: Climate anomalies across the whole timeseries](display/climvars_anomalies_fullseries.png)
\newpage

@@

- Data cleaning steps
- Calculating DBH equation
- Corroboration with tape measurements
- error distribution

@@

## Individual growth and correlations

- Negative growth proportions across the years

@@

<!-- ## Individual model diagnostics

To add:

\newpage -->

## Growth occurrence models

To add: zero growth models
